Notes on Wide Gap

### 2016-04-11 paper/wide_gap_notes.tex
parasitic mode comment
expanding nonlinear terms: N2 psi
N3 psi
N2 u
N3 u
N2A and N3A
N2B and N3B
updated narrow to wide gap section for chain rule notes.

@@

\beq
\mathbf{N} = \left[\begin{matrix}
J\left(\Psi, \frac{1}{r^2} \left(\nabla^2 \Psi - \frac{2}{r}\partial_r \Psi \right) \right) - \frac{2}{\beta} J \left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_r A\right)\right) - \frac{2}{r} u_\phi \partial_z u_\phi + \frac{2}{\beta} \frac{2}{r} B_\phi \partial_z B_\phi \\
\frac{1}{r} J \left(\Psi, u_\phi\right) - \frac{1}{r} \frac{2}{\beta} J \left(A, B_\phi\right) + \frac{1}{r^2} u_\phi \partial_z \Psi - \frac{2}{\beta} \frac{1}{r^2} B_\phi \partial_z A \\
-\frac{1}{r} J \left(A, \Psi\right)\\
-\frac{1}{r} J \left(A, u_\phi\right) - \frac{1}{r} J \left(B_\phi, \Psi\right) - \frac{1}{r^2} B_\phi \partial_z \Psi + \frac{1}{r^2} u_\phi \partial_z A
\end{matrix}\right] 
\eeq

@@

@@

\begin{equation}
  \label{eq:del_scalar}
  \nabla \psi = \frac{\partial \psi}{\partial r} \rhat + \frac{1}{r} \frac{\partial \psi}{\partial \phi} \phihat + \frac{\partial \psi}{\partial z} \zhat.
\end{equation}

>>>>

In order to recover the narrow gap, we take the transformation from dimensional, cylindrical coordinates $(\widetilde{r},\widetilde{z})$ to dimensioneless quantities $(x,z)$. In order to do so, we use $\widetilde{r} = r_0 (1 + \delta x)$, where $\delta = (r_{out} - r_{in})/r_0 \to 0$. Then, we recall that we must change all derivatives $\partial_{\widetilde{r}} \psi = \partial_x \psi \partial_{\widetilde{r}} x$ and likewise for $\partial_{\widetilde{z}}$. In order that the $x$ and $z$ parts of the equations come in at the same order, we must choose $\widetilde{z} = r_0 \delta z$. Then, $\partial_{\widetilde{r}} x = \delta^{-1}$ and $\partial_{\widetilde{z}} z = \delta^{-1}$. When you finally expand out all terms, you should see that everything that is not $\partial^2_x$ and $\partial^2_z$ will be at higher order in $\delta$, and thus will go to zero. For example, just taking the scalar Laplacian of $B_\phi$,

\begin{equation}
  \nabla^2 B_\phi = \frac{1}{r} \frac{\partial}{\partial r}\left(r \frac{\partial \psi}{\partial r} \right) + \frac{\partial^2 \psi}{\partial z^2}
\end{equation}

gives

\begin{equation}
  \frac{1}{(1 + \delta x)} \delta^{-2} \partial_x \left[(1 + \delta x) \partial_x B_\psi \right] + \delta^{-2} \partial_z^2 B_\phi,
\end{equation}
and using the binomial expansion,

\begin{equation}
  (1 - \delta x) \delta^{-2} \left(\partial_x^2 B_\psi + \delta \partial_x B_\psi + \delta x \partial_x^2 B_\psi \right) + \delta^{-2} \partial_z^2 B_\phi.
\end{equation}

When $\delta \to 0$, this leaves

\begin{equation}
  \partial_x^2 B_\phi + \partial_z^2 B_\phi,
\end{equation}
as expected. Of course, we'd also do $B_\phi \to B_y$ at the same time.

@@

\beq\label{eq:nonlinearvector}
\mathbf{N} = \left[\begin{matrix}
J\left(\Psi, \frac{1}{r^2} \left(\nabla^2 \Psi - \frac{2}{r}\partial_r \Psi \right) \right) - \frac{2}{\beta} J \left(A, \frac{1}{r^2} \left( \nabla^2 A - \frac{2}{r} \partial_r A\right)\right) - \frac{2}{r} u_\phi \partial_z u_\phi + \frac{2}{\beta} \frac{2}{r} B_\phi \partial_z B_\phi \\
\frac{1}{r} J \left(\Psi, u_\phi\right) - \frac{1}{r} \frac{2}{\beta} J \left(A, B_\phi\right) + \frac{1}{r^2} u_\phi \partial_z \Psi - \frac{2}{\beta} \frac{1}{r^2} B_\phi \partial_z A \\
-\frac{1}{r} J \left(A, \Psi\right)\\
-\frac{1}{r} J \left(A, u_\phi\right) - \frac{1}{r} J \left(B_\phi, \Psi\right) - \frac{1}{r^2} B_\phi \partial_z \Psi + \frac{1}{r^2} u_\phi \partial_z A
\end{matrix}\right] 
\eeq

@@

\section{Expansion of Nonlinear Terms}

Expanding the terms in Equation \ref{eq:nonlinearvector}, we find.

\beq
\mathbf{N} = \epsilon^2 \mathbf{N}_2 + \epsilon^3 \mathbf{N}_3
\eeq

\beq
\begin{split}
N_2^{\Psi} & = J\left(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1\right) + J\left(\Psi_1, -\frac{2}{r^3}\partial_r\Psi_1\right) \\
&- \frac{2}{\beta} J \left(A_1, \frac{1}{r^2} \nabla^2 A_1\right) - \frac{2}{\beta} J\left(A_1, -\frac{2}{r^3} \partial_r A_1\right) - \frac{2}{r} u_1 \partial_z u_1 + \frac{2}{\beta} \frac{2}{r} B_1 \partial_z B_1
\end{split}
\eeq

\beq
\begin{split}
N_3^{\Psi} & = J\left(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_2\right) + J\left(\Psi_2, \frac{1}{r^2} \nabla^2\Psi_1\right) + 2 J \left(\Psi_1, \frac{1}{r^2}\partial_Z\partial_z \Psi_1\right) \\
&+ J\left(\Psi_1, -\frac{2}{r^3}\partial_r \Psi_2\right) + J\left(\Psi_2, -\frac{2}{r^3}\partial_r \Psi_1\right) + \widetilde{J}\left(\Psi_1, \frac{1}{r^2} \nabla^2 \Psi_1\right) + \widetilde{J} \left(\Psi_1, -\frac{2}{r^3}\partial_r \Psi_1\right)\\
& - \frac{2}{\beta} J\left(A_1, \frac{1}{r^2}\nabla^2 A_2\right) - \frac{2}{\beta} J\left(A_2, \frac{1}{r^2}\nabla^2 A_1\right) - \frac{4}{\beta} J\left(A_1, \frac{1}{r^2}\partial_Z\partial_z A_1\right) - \frac{2}{\beta} J\left(A_1, -\frac{2}{r^3} \partial_r A_2 \right) \\
& - \frac{2}{\beta} J\left(A_2, -\frac{2}{r^3} \partial_r A_1\right) - \frac{2}{\beta} \widetilde{J} \left(A_1, \frac{1}{r^2} \nabla^2 A_1\right) - \frac{2}{\beta} \widetilde{J} \left(A_1, -\frac{2}{r^3} \partial_r A_1\right) \\
& - \frac{2}{r} u_1 \partial_z u_2 - \frac{2}{r} u_2 \partial_z u_1 - \frac{2}{r} u_1 \partial_Z u_1 + \frac{2}{\beta}\frac{2}{r} B_1\partial_z B_2 + \frac{2}{\beta}\frac{2}{r} B_2 \partial_z B_1 + \frac{2}{\beta} \frac{2}{r} B_1 \partial_Z B_1
\end{split}
\eeq

\beq
\begin{split}
N_2^{u} = \frac{1}{r} J\left(\Psi_1, u_1\right) - \frac{1}{r} \frac{2}{\beta} J\left(A_1, B_1\right) + \frac{1}{r^2} u_1 \partial_z \Psi_1 - \frac{2}{\beta}\frac{1}{r^2} B_1 \partial_z A_1
\end{split}
\eeq

\beq
\begin{split}
N_3^u & = \frac{1}{r}J\left(\Psi_1, u_2\right) + \frac{1}{r}J\left(\Psi_2, u_1\right) + \frac{1}{r}\widetilde{J} \left(\Psi_1, u_1\right) \\
& - \frac{1}{r}\frac{2}{\beta} J\left(A_1, B_2\right) - \frac{1}{r} \frac{2}{\beta} J\left(A_2, B_1\right) - \frac{1}{r}\frac{2}{\beta}\widetilde{J}\left(A_1, B_1\right) \\
& + \frac{1}{r^2} u_1\partial_z \Psi_2 + \frac{1}{r^2} u_2 \partial_z \Psi_1 + \frac{1}{r^2} u_1 \partial_Z \Psi_1 \\
& - \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_z A_2 - \frac{2}{\beta} \frac{1}{r^2} B_2 \partial_z A_1 - \frac{2}{\beta} \frac{1}{r^2} B_1 \partial_Z A_1
\end{split}
\eeq

\beq
N_2^A = -\frac{1}{r} J\left(A_1, \Psi_1\right)
\eeq

\beq
N_3^A = -\frac{1}{r} J\left(A_1, \Psi_2\right) - \frac{1}{r}J\left(A_2, \Psi_1\right) - \frac{1}{r} \widetilde{J}\left(A_1, \Psi_1\right)
\eeq

\beq
N_2^B = -\frac{1}{r} J\left(A_1, u_1\right) - \frac{1}{r} J\left(B_1, \Psi_1\right) - \frac{1}{r^2} B_1 \partial_z \Psi_1 + \frac{1}{r^2} u_1 \partial_z A_1
\eeq

\beq
\begin{split}
N_3^B & = - \frac{1}{r} J\left(A_1, u_2\right) - \frac{1}{r} J\left(A_2, u_1\right) - \frac{1}{r}\widetilde{J}\left(A_1, u_1\right) \\
& - \frac{1}{r} J\left(B_1, \Psi_2\right) - \frac{1}{r} J\left(B_2, \Psi_1\right) - \frac{1}{r} \widetilde{J} \left(B_1, u_1\right) \\
& - \frac{1}{r^2} B_1\partial_z \Psi_2 - \frac{1}{r^2} B_2 \partial_z \Psi_1 - \frac{1}{r^2} B_1 \partial_Z \Psi_1 \\
& + \frac{1}{r^2} u_1 \partial_z A_2 + \frac{1}{r^2} u_2 \partial_z A_1 + \frac{1}{r^2} u_1 \partial_Z A_1
\end{split}
\eeq

\section{Notes for paper}

-- Comment on channel mode formation w.r.t. parasitic modes?

@@

\begin{equation}
  \label{eq:del_scalar}
  \nabla \psi = \frac{\partial \psi}{\partial r} \rhat + \frac{1}{r} \frac{\partial \psi}{\partial \phi} \phihat + \frac{\partial \psi}{\partial z} \zhat,
\end{equation}

\begin{equation}
  \label{eq:del2_scalar}
  \nabla^2 \psi = \frac{1}{r} \frac{\partial}{\partial r}\left(r \frac{\partial \psi}{\partial r} \right) + \frac{1}{r^2} \frac{\partial^2 \psi}{\partial \phi^2} + \frac{\partial^2 \psi}{\partial z^2},
\end{equation}
